Homework 4: Centrality Analysis of the Florentine Wedding dataset

### 2022-02-17 _academics/ps753-hw4/ps753-hw4.Rmd
Update yaml description

---
title: "Homework 4: Centrality Analysis of the Florentine Wedding dataset"
description: |
  A first-look network analysis
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-09
output:
  distill::distill_article:
    self_contained: false
    code_folding: true
categories:
  - r
  - social networks
---

>>>>

---
title: "Homework 4: Centrality Analysis of the Florentine Wedding dataset"
description: |
  Examining centrality measures in the Florentine network
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-09
output:
  distill::distill_article:
    self_contained: false
    code_folding: true
    toc: true
categories:
  - r
  - social networks
---
